The Changing Shape of Empire: A GM Study of Chimú Bottles in Museum Collections

### 2022-01-27 supp/01-linear.Rmd
<edit readme>

```{r load packages 3, echo=TRUE}
# install required analysis packages
devtools::install_github("tidyverse/tidyverse")
devtools::install_github("mlcollyer/RRPP")
devtools::install_github("kassambara/ggpubr")
devtools::install_github('sinhrks/ggfortify')
# load libraries
library(here)
library(tidyverse)
library(RRPP)
library(ggpubr)
library(ggfortify)
library(cluster)
library(wesanderson)
library(ggExtra)
```

>>>>

```{r load packages 3, echo=TRUE}
# install required analysis packages
#devtools::install_github("tidyverse/tidyverse")
#devtools::install_github("mlcollyer/RRPP")
#devtools::install_github("kassambara/ggpubr")
#devtools::install_github('sinhrks/ggfortify')
# load libraries
library(here)
library(tidyverse)
library(RRPP)
library(ggpubr)
library(ggfortify)
library(cluster)
library(wesanderson)
library(ggExtra)
```

### 2022-01-27 supp/index.Rmd
<edit readme>

--- 
title: "Supplementary materials for paper: The Changing Shape of Empire: A GM Study of Chimú Bottles in Museum Collections"
author: "R. Alan Covey, Robert Z. Selden Jr., Nicole Payntar, and Astrid Runggaldier"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
description: "Differences in Chimú vessel shape."
---

@@

 *

@@

Components of the undertaking presented in this volume are novel, and this basic research endeavour is rooted in archaeological epistemology. Sharing data is not enough, and if investigators share only data absent their analysis code, that places a substantive burden on those who may seek to build upon or replicate their work in the future. In this instance, the choice to pursue a replicable work flow occurs based on the simple fact that this work is foundational, and meant to begin a meaningful discussion related to projectile morphology.

>>>>

--- 
title: "The Changing Shape of Empire: A GM Study of Chimú Bottles in Museum Collections"
author: "R. Alan Covey, Robert Z. Selden Jr., Nicole Payntar, and Astrid Runggaldier"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
description: "Differences in Chimú vessel shape."
---

@@

### Linear metrics

 * Bottles and jars **differ significantly** in orifice diameter
 * Bottles and jars **differ significantly** in belly diameter

```{r botjarbox, out.width = "100%", dpi = 300, echo=FALSE, warning=FALSE, fig.cap="Boxplots for vessel form by a, orifice diameter; b, base diameter; c, neck diameter; d, belly diameter; e, height; and f, rim thickness."}
knitr::include_graphics('images/boxsite-1.png')
```

### Geometric morphometrics

 * Bottles and jars **differ significantly** in shape
 * Bottles and jars do not differ in size

```{r botjar, out.width = "100%", dpi = 300, echo=FALSE, warning=FALSE, fig.cap="Mean shapes for bottles (a), jars (c), and comparison of bottle (gray) and jar (black) shape (b)."}
knitr::include_graphics('images/mshape.png')
```

@@
